---
title: "Diamond Data Analysis"
author: "Tejaswi G"
date: "15-04-24"
output: html_document
---

```{r setup, include=FALSE,echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
```

## Introduction

Here, I am covering Exploratory Data Analysis. Specifically, we'll use data visualization and transformation to explore the 'diamonds' data set.

1. What type of variation occours within my variables?
2. What type of covariation occours between my variables?

```{r, echo = FALSE}
glimpse(diamonds)
```


## Variation

- Categorical Variables
```{r bar_plot, fig.cap = "Bar CHart Looking at Diamond Cut"}
ggplot(diamonds) + geom_bar(aes(x=cut))
```

```{r cut_count}
diamonds %>% count(cut)
```
- Continuous Variables

```{r hist_carat}
ggplot(diamonds) + geom_histogram(aes(x = carat),binwidth = 0.5)
```
## Data Cleaning

```{r small_dataset_creation}
small <- diamonds %>% filter(carat < 3)
```

```{r small_hist}
ggplot(small, aes(x=carat)) + geom_histogram(binwidth = 0.1)
```
## Typical Values

1. Which values are the most common? Why?
2. Which  values are rare? Why Does that match your expectations?
3. Can you see any unusual patterns that might explain them?

```{r}
ggplot(small,aes(x = carat)) + geom_histogram(binwidth = 0.01)
```
**Questions that needs to be answered**
-Why are more diamonds at whole carats?
-Why are there more diamonds that are more than the right of the common carats?

## Covariation

### Categorical vs Continuous

```{r}
ggplot(diamonds) + geom_bar(aes(x=cut))
```

```{r}
ggplot(diamonds, aes(x=price)) + geom_freqpoly(aes(color = cut),binwdth=500)
```
-Boxplot
```{r}
ggplot(diamonds, aes(x = cut, y = price)) + geom_boxplot()
```


### Categorical vs Categorical 

```{r}
diamonds %>% count(color, cut) %>% ggplot(aes(x=color, y = cut)) + geom_tile(aes(fill=n))
```

### Continuous vs Continuous 
```{r}
ggplot(diamonds) + geom_point(aes(x=carat, y=price), alpha=1/100)
```
```{r}
ggplot(diamonds) + geom_hex(aes(x=carat, y = price))
```
```{r}
ggplot(diamonds, aes(x=carat, y=price)) + geom_boxplot(aes(group=cut_width(carat, 0.1)))
```
### Pattern and Models

```{r}
mod <- lm(log(price) ~ log(carat), data = diamonds)
```

```{r summary_mod}
summary(mod)
```




